Universal Anonymous Signatures

### 2022-06-22 prism-backend/research/gsac/formal-uas.tex
Small pass.

The main contribution of this section is giving a simple syntax and model that
still allow spanning a wide variety of related schemes. We combine aspects of GS
and AC schemes -- and, therefore, rely heavily on previous works --,
generalizing whenever possible. Like in ACs, there are multiple issuers, and
each user can get one or more credentials from any of them. We incorporate
openers, as in GSs, but there is no tight relationship between issuer
and opener. Signing and verification are non-interactive processes like in GS
schemes, but we show how to convert to an interactive one like in ACs. Finally,
we incorporate functions that allow tweaking the behaviour at issuance,
signature generation, and verification times; while signatures contain all the
necessary information to check that all computations are performed correctly.

@@

\paragraph{Issuance, evaluation, and opening functions.} %
We emphasize that, both in our syntax definition, as well as on the following
modelling, we make use of three different and abstract functions: \fissue,
\feval and \finsp. The three functions are introduced to allow customized
governance of the resulting instantiation of an \UAS scheme. They will be
defined by different parties, but in all cases, they are run by users (maybe,
on user-private data). Also, in all cases, the user has to prove correctness of
their computation. We introduce them next, and give concrete examples for
building specific well-known restrictions of \UAS in
\secref{sec:transformations}.

\begin{description}
\item[$\fissue: (\usk,\scred,\attrs)
  \rightarrow 0/1$.] Chosen by issuers within a family of functions \famfissue,
  the issuance function defines what customized conditions an issuer requires
  in order to issue credentials, when receiving a request from user with secret
  key \usk, for attributes \attrs. \fissue may run checks on a (possibly empty)
  set of additional credentials \scred, all bound to \usk, and possibly
  issued by other issuers. \fissue returns $1$ to accept a request, $0$ to
  reject it.
\item[$\feval: (\usk,\scred,\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user secret key \usk, credentials \scred, and message to be signed
  \msg. \feval can be used to control the information related to the signer that
  will be revealed alongside a signature, and to modulate the behaviour of
  \finsp. Its outputs two values, $\yeval^0$ and $\yeval^1$, where the former
  is revealed in plaintext along with the signature, and $\yeval^1$ is encrypted
  and used to modulate the behaviour of \finsp. Both values must belong in a
  well defined set \rngfeval. For readability, we write
  $\Yeval = (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\usk,\scred,\msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value, derived from the user's secret key,
  credentials, and signed message, should be extractable by an opener.
  Note that \finsp also receives as input a value in the range of the \feval
  function, $\rngfeval^2$. This allows opening logic to depend on the values
  produced by the evaluation function. The output of \finsp is a value
  \yinsp, which must belong in a well defined set \rngfinsp.
\end{description}

We emphasize that, even though \finsp and \feval seem redundant, they are not.
To see this, observe that \finsp is defined by openers, and will be fixed in
all signatures that can be opened by the opener who defined it. On the other
hand, \feval can be defined by (e.g.) verifiers on a per-signature basis, even
if the signatures use the same \finsp. Thus, \feval can be programmed to contain
the conditions set by (e.g.) verifiers for signatures they receive; whereas
\finsp can be programmed to extract specific utility values when needed, which
may depend on the checks required by the verifier a signature was intended to.

@@

\subsection{Model for \UAS Schemes}
\label{ssec:model-uas}

We now define our model for Universal Anonymous Signatures. Property-wise, we
maintain anonymity, non-frameability, and include two extra unforgeability
properties: unforgeability of issuance, which ensures that issuance policies
are not circumvented; and unforgeability of signatures, guaranteeing that
signature evaluation policies are respected, as well as soundness of opening.

From a functional perspective, we require that each issuer and opener fix
the issuance predicate \fissue and opener function \finsp when generating
their public keys. On the other hand, signature evaluation functions \feval can
be defined at signing time. This is in line with the usual practice in anonymous
credentials, that let
users prove arbitrary claims on their credentials, as long as they are met by
the contained attributes. In practice, most probably, the signature evaluation
policy to be
employed in each signature will be defined by the verifier (or jointly between
user and verifier), including the specification of which opener will be
able to post-process signatures\footnote{See, for instance, the concept of
  presentation exchanges, or requests, in the context of Verifiable Credentials:
  \url{https://identity.foundation/presentation-exchange/} (last access, May
  5th, 2022).}. Beyond these general policies, which already give much
flexibility, the syntax for \UAS supports multiple issuers and openers, and
lets users leverage multiple credentials to request issuance of new ones, and
to produce signatures.

\paragraph{Global Variables.} %
The environment manages several global variables in the games posed to the
adversary. Users are referred to with user identifiers, \uid; for credentials,
we use \cid; for issuers, \iid; and for openers, \oid. In all cases, we use bold
font to denote sets: e.g., \scid and \siid denote sets of credential and issuer
identifiers. All tables/sets are initialized as empty tables/sets.

\begin{description}
\item[Sets for parties]:
  \begin{description}
  \item[\HU and \CU.] Keep track of honest (\HU) and corrupted (\CU) users;
    i.e., they are sets of {\uid}s.
  \item[\HI and \CI.] Keep track of honest (\HI) and corrupted (\CI) issuers;
    i.e., they are sets of {\iid}s.
  \item[\HO and \CO.] Keep track of honest (\HO) and corrupted (\CO) openers;
    i.e., they are sets of {\oid}s.
  \end{description}
\item[Tables for keys]:
  \begin{description}
  \item[\UK.] \UK maintains user keys $\usk$. To refer to the key of a specific
    user, we use $\UK[\uid]$. 
  \item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
    $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
    use \PUBIK to refer to the public component, which also includes the \fissue
    function; and \PRVIK refers to the private component of the key pair.
  \item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for opener key pairs. Instead
    of \fissue, \OK includes the \finsp function.
  \end{description}
\item[Tables for credentials-related data]:
  \begin{description}
  \item[\CRED.] Stores information related to credentials obtained by users in
    the system. Thus, it is indexable by \cid. More specifically, it stores
    tuples of the form $(\uid,\cred,\iid,\attrs,\scid)$, where \uid is the
    identity of the owner of the credential, \cred (when available) is the
    credential itself, \iid is the identifier of the credential issuer, \attrs
    are the attributes included in \cred, and \scid are the identifiers of the
    credentials (if any) that \uid used to request \cred. For notational
    convenience, we may use $\CRED[\scid]$ to refer to $\CRED[\cid]$ for all
    $\cid \in \scid$. Also, when clear from context, we sometimes use
    $\CRED[\cid]$ (resp. $\CRED[\scid]$ to mean \cred (resp. \scred) in
    $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,\cdot)$ (resp. $\CRED[\scid]$).
  \item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
    ``\uid such that $\CRED[\cid] = (\uid, \cdot, \cdot, \cdot, \cdot)$''.
  \item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
    ``\attrs such that $\CRED[\cid] = (\cdot, \cdot, \cdot, \attrs, \cdot)$''.
  \item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
    ``\iid such that $\CRED[\cid] = (\cdot, \iid, \cdot, \cdot, \cdot)$''.
  \end{description}
\item[Tables for signatures]:
  \begin{description}
  \item[\SIG.] Maintains signatures generated via the \SIGN oracle, on behalf
    of honest users. Entries of this table are $(\oid,\scid,\sig,\Yeval,\msg,
    \feval)$, where \oid is the opener chosen for the signature, \scid is the
    set of credentials used for signing, \feval is the signing evaluation
    function, and \sig and \msg are the produced signature and signed message.
  \item[\CSIG.] Maintains challenge signatures output to the adversary; i.e.,
    the table is indexable by challenge signatures \csig.
    Each entry contains also $\cuid_b$ and $\scid_b$ the challenge user and
    credential identifiers set used to produce \csig; as well as the
    corresponding challenge user and credential set indexed by the complementary
    $1-b$; the signed message \msg and signing evaluation function \feval, the
    result of \feval, \yeval, and the opener identifier \oid.
  \end{description}
\end{description}

@@

\begin{description}
\item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
  the associated issuance function.
\item[\OGEN.] Adds a new opener to the game, generating its key pair and
  setting the associated evaluation and inspection functions.
\item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
  key to the adversary.
\item[\OCORR.] Corrupts an existing (and honest) opener, by giving its secret
  key to the adversary.  
\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
  the user's key pair.
\item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
  user already exists and is honest, corrupts it, leaking its key and
  credentials.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer
  in games that support it, by letting it interact with honest users who want to
  receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, outputs the result of the
  opening function, along with a correctness proof.
\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
  singing evaluation function and a message, returns a signature produced by one
  of these two user and credential sets, defined by the bit $b$, which is
  established in the anonymity game.
\end{description}

@@

\paragraph{Helper functions \ExtractIssue, \ExtractSign, \IdentifyCred, and
  \IdentifyUK.} In our modelling, we assume the existence of fhese four
functions. They are not
functions available in the actual scheme, but rather to the challenger in the
experiments we use to formalize security of \UAS schemes. Similar techniques
have been used before to prove security in privacy-preserving schemes with some
sort of accountability, but that do not offer conventional opening as vanilla
group signatures. For instance, see related works on DAA \cite{bfg+11,cdl16} and
group signature variants \cite{dl21,fgl21,gl19,lnpy21}. More concretely, these
functions are as follows:

\begin{description}
\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\attrs_{\scred},\scred)$.]
  Receives an $\langle \Obtain, \Issue \rangle$ transcript, and returns the
  credentials (if any) and their attributes that were involved
  in the request. It clearly needs an honest issuer as, otherwise, the
  transcripts won't be available. Consequently, we only use it to define the
  properties that require an honest issuer.
\item[$\ExtractSign(\oid,\siid,\Sig,\msg,\feval) \rightarrow (\usk,
  \scred,\attrs_{\scred},\yeval^1,\yinsp)$.] Receives a signature \Sig,
  as well as the opener identifier \oid, and the identifiers of all issuers of
  the credentials used to produce the signature over \msg, and for \feval. It
  outputs the user secret key and credentials (with their attributes) used to
  generate the signature, and the value returned by the opening fuction.
\item[$\IdentifyCred(\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
  issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
  Otherwise, it returns $0$. In order to be meaningful, this requires that,
  for every $(\attrs_{\cred},\cred)$ pair, there is at most one \usk that makes
  \IdentifyCred return $1$.
\item[$\IdentifyUK(\uid,\usk)$.] Returns $1$ is \usk is {\uid}'s secret key.
  This is trivial for honest users, for which there must be a one-to-one
  relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
  to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
  to \uid, extract the used secret key, and check if there is a match. Note that
  this does not guarantee that there will be only one \usk per corrupt \uid,
  though. Also, when used for corrupt users, this can only be used when the
  issuer is honest, as transcripts are needed. 
\end{description}

Note that, for all the helper functions, in the case of credentials, transcripts,
and signatures by honest users, it is enough to have access to the corresponding
state information (described below) maintained by the challenger in our
experiments. For credentials and join transcripts of corrupt users, or
dishonestly produced signatures, we do need to perform actual extraction.
Certainly, the challenger
needs special knowledge/power such as decryption trapdoors, the ability to
rewind the game, or program random oracles. The approach needs thus to depend on
the concrete construction. \jdv{Although, for the case of \ExtractIssue and
  \IdentifyUK, online extractability (or alternative requirements, such as
  non-parallel or logarithmic number of joins) is necessary.}

\paragraph{Correctness.} %
Correctness of \UAS schemes is formalized through the experiment in
\figref{fig:exp-uas-corr}. It states that a signature over any arbitrary message
and valid function \feval, produced honestly leveraging credential set \scid,
owned by user \uid, is accepted by \Verify. Moreover, all the credentials in
\scid meet the conditions set by the corresponding \fissue defined by the issuer
which issued each credential. Similarly, the output \yeval of \feval matches the
value produced by \Sign alongside with \sig; and the value produced by \Open
is accepted by \Judge, and matches the output of applying \finsp on \yeval, the
credentials, user key, and message.

@@

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      \cid \gets \adv^{\Oforgeissue}(\parm) \\
      \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 0 \\
      \textrm{Parse}~\CRED[\cid]~\textrm{as}~(\cdot,\cdot,\iid,\cdot,\cdot);~
      \IK[\iid]~\textrm{as}~((\ipk,\fissue),\cdot) \\
      (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trans[\cid]) \\
      \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
      \exists \cred \in \scred~\suchthat~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0: \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of credential issuance in \UAS schemes.}
  \label{fig:exp-uas-unfor-issue}
\end{figure}

>>>>

The main contribution of this section is giving a simple syntax and model that
still allow spanning a wide variety of related schemes. We combine aspects of GS
and AC schemes, generalizing whenever possible. Like in ACs, there are multiple
issuers, and each user can get one or more credentials from any of them; and,
also, use more than one credential simultaneously to produce a signature. We
incorporate openers, as in GSs, but there is no tight relationship between
issuer and opener. As a consequence, signers (potentially along with verifiers)
may choose, on a per-signature basis, the policies governing the utility
information extractable from a signature. Signing and verification are
non-interactive processes like in GS schemes, but we show how to convert to an
interactive one as in ACs. Finally, we incorporate functions that allow
tweaking the conditions checked at credential issuance and signature generation
times, including the information that an opener will be able to extract from a
signature. This flexibilizes the scheme even beyond the loose relationship
between issuer and opener.

@@

\paragraph{Issuance, evaluation, and opening functions.} %
We introduce three functions in our syntax and model. Through them,
it is possible to modulate the behaviour of the resulting instantiation, by
controling the conditions upon which a new credential can be issued, or the
information revealed at signing time, or after signing. In all cases, it is
the user who computes them, and has to prove correctness of such computation.
We give concrete examples in \secref{sec:relationships}, and define them next:

\begin{description}
\item[$\fissue: (\usk,\scred,\attrs)
  \rightarrow 0/1$.] Chosen by each issuer within a family of functions
  \famfissue, the issuance function defines the customized conditions required
  by the issuer to grant a credential over attributes \attrs, when requested by
  a user with secret key \usk, potentially leveraging a set of previously
  obtained credentials \scred. \fissue returns $1$ to accept a request, $0$ to
  reject it.
\item[$\feval: (\usk,\scred,\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user secret key \usk, credentials \scred, and message to be signed
  \msg. \feval outputs two values, $\yeval^0$ and $\yeval^1$, where the former
  is revealed in plaintext along with the signature, and $\yeval^1$ is
  encrypted. Both can be used to modulate the bevahiour of \finsp, and must
  belong in a well defined set \rngfeval. For readability, we write $\Yeval =
  (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\usk,\scred,\msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value, derived from the user's secret key,
  credentials, and signed message, should be extractable by an opener. Its
  behaviour can be modulated by \Yeval, and its output a value \yinsp, which
  must belong in a well defined set \rngfinsp.
\end{description}

\feval and \finsp may seem redundant. However, observe that the former is chosen
on a per-signature basis, and probably after negotiation between signer and
verifier. As such, it governs the information revealed at signing time. On the
other hand, \finsp governs the information that may be revealed after signing.
Moreover, it is defined by openers, and even though signers and verifiers
may negotiate to use any opener for a given signature, it is not possible for
an opener to change the chosen function.

@@

\subsection{Security Model}
\label{ssec:model-uas}

We define the security expected from an \UAS scheme using a game-based approach.
An \UAS scheme must ensure privacy at credential issuance, meaning that two
runs of the credential issuance protocol should not leak any information beyond
necessary about the user requesting the credential. Note that this is now
crucial for privacy since, as AC schemes, \UAS allows multiple credentials per
user -- thus, knowing what credential a user requests can lead to user
profiling. It must also ensure signature privacy, meaning that no information
can be learned, from a signature, by third parties beyond what the user agrees
to reveal, and what may be extractable by the chosen opener.
Issuance unforgeability requires that \UAS schemes ensure that the claims used
to support a credential request cannot be falsified (issuance unforgeability).
Similarly, signature unforgeability requires that no adversary should be able to
falsify the correctness proofs for the claims included in the signatures. In
both cases (issuance and signature unforgeability), we introduce the notion of
traceability in GS, requiring that all credentials involved in the corresponding
process have to be associated to a known user. Finally, \UAS schemes inherit the
useful non-frameability property of GS schemes which, even in the worst-case
scenario of having a corrupt issuer. In this case, although we cannot ensure
anything regarding correctness of the claims, we can ensure that no honest user
can be framed with having created a signature that s/he did not create --
although the concept may get a bit blurred, as there is no traditional opening.
%
We describe next the global variables and oracles that we use in our modelling.

\paragraph{Global Variables.} %
Users are referred to with user identifiers, \uid; for credentials, we use \cid;
for issuers, \iid; and for openers, \oid. In all cases, we use bold font to
denote sets: e.g., \scid and \siid denote sets of credential and issuer
identifiers. All tables/sets are initialized as empty tables/sets.

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of honest users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of corrupt users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.    
\item[\UK.] \UK maintains user keys $\usk$. To refer to the key of a specific
  user, we use $\UK[\uid]$. 
\item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
  $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
  use \PUBIK to refer to the public component, which also includes the \fissue
  function; and \PRVIK refers to the private component of the key pair.
\item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for opener key pairs. Instead
  of \fissue, \OK includes the \finsp function.
\item[\CRED.] Stores information related to credentials obtained by users in
  the system. Thus, it is indexable by \cid. More specifically, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,\scid,\siid)$, where \uid is the
  identity of the owner of the credential, \cred (when available) is the
  credential itself, \iid is the identifier of the credential issuer, \attrs
  are the attributes included in \cred, \scid are the identifiers of the
  credentials (if any) that \uid used to request \cred, and \siid the issuers
  of those credentials. For notational
  convenience, we may use $\CRED[\scid]$ to refer to $\CRED[\cid]$ for all
  $\cid \in \scid$. Also, when clear from context, we sometimes use
  $\CRED[\cid]$ (resp. $\CRED[\scid]$ to mean \cred (resp. \scred) in
  $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but keeps track of challenge credentials in the
  issuance anonymity game.
\item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid, \cdot, \cdot, \cdot, \cdot)$''.
\item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot, \cdot, \cdot, \attrs, \cdot)$''.
\item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot, \iid, \cdot, \cdot, \cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Maintains challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

@@

\begin{description}
\item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
  the associated issuance function.
\item[\OGEN.] Adds a new opener to the game, generating its key pair and
  setting the associated evaluation and inspection functions.
\item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
  key to the adversary.
\item[\OCORR.] Corrupts an existing (and honest) opener, by giving its secret
  key to the adversary.  
\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
  the user's key pair.
\item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
  user already exists and is honest, corrupts it, leaking its key and
  credentials.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer, by
  letting it interact with honest users who want to receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, outputs the result of the
  opening function, along with a correctness proof.
\item[\OBTCHALb.] Upon receiving a target credential identifier, two challenge
  users and credential sets, an honest issuer identifier, and a set of
  attributes, issues a credential for the challenge user and credential set
  defined by the bit $b$. 
\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
  singing evaluation function and a message, returns a signature produced by one
  of these two user and credential sets, defined by the bit $b$.
\end{description}

@@

\paragraph{Helper functions \ExtractIssue, \ExtractSign, \IdentifyCred, and
  \IdentifyUK.} We assume the existence of these four functions. They are not
functions available in the actual scheme, but rather to the challenger in the
experiments we use to formalize security of \UAS schemes. Similar techniques
have been used before to prove security in privacy-preserving schemes with some
sort of accountability, but that do not offer conventional opening as vanilla
group signatures. For instance, see related works on DAA \cite{bfg+11,cdl16} and
group signature variants \cite{dl21,fgl21,gl19,lnpy21}. More concretely, these
functions are as follows:

\begin{description}
\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\attrs_{\scred},\scred)$.]
  Receives an $\langle \Obtain, \Issue \rangle$ transcript, and returns the
  credentials (if any) and their attributes involved in the request. It 
  needs an honest issuer as, otherwise, the transcripts won't be available.
\item[$\ExtractSign(\oid,\siid,\Sig,\msg,\feval) \rightarrow (\usk,
  \scred,\attrs_{\scred},\yeval^1,\yinsp)$.] Receives a signature \Sig,
  as well as the opener identifier \oid, and the identifiers of all issuers of
  the credentials used to produce the signature over \msg, and for \feval.
  It outputs the user secret key and credentials (with their attributes) used to
  generate the signature, and the $\yeval^1$ and \yinsp values.
\item[$\IdentifyCred(\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
  issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
  Otherwise, it returns $0$. In order to be meaningful, this requires that,
  for every $(\attrs_{\cred},\cred)$ pair, there is at most one \usk that makes
  \IdentifyCred return $1$.
\item[$\IdentifyUK(\uid,\usk)$.] Returns $1$ is \usk is {\uid}'s secret key.
  This is trivial for honest users, for which there must be a one-to-one
  relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
  to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
  to \uid, extract the used secret key, and check if there is a match. In the
  latter case, there is no guarantee of getting a one-to-one relationship
  between \usk and \uid. Also, when used for corrupt users, this can only be
  used when the issuer is honest, as transcripts are needed. 
\end{description}

% Note that, for all the helper functions, in the case of credentials, transcripts,
% and signatures by honest users, it is enough to have access to the corresponding
% state information (described below) maintained by the challenger in our
% experiments. For credentials and join transcripts of corrupt users, or
% dishonestly produced signatures, we do need to perform actual extraction.
% Certainly, the challenger
% needs special knowledge/power such as decryption trapdoors, the ability to
% rewind the game, or program random oracles. The approach needs thus to depend on
% the concrete construction. \jdv{Although, for the case of \ExtractIssue and
%   \IdentifyUK, online extractability (or alternative requirements, such as
%   non-parallel or logarithmic number of joins) is necessary.}

\paragraph{Correctness.} %
Correctness of \UAS schemes is formalized through the experiment in
\figref{fig:exp-uas-corr}. It states that a signature over any arbitrary message
and valid function \feval, produced honestly leveraging credential set \scid,
owned by user \uid, is accepted by \Verify. Moreover, all the credentials in
\scid meet the conditions set by the corresponding \fissue defined by the issuer
which issued each credential. Similarly, the output of \feval matches the
value produced by \Sign alongside with \sig; and the value produced by \Open
is accepted by \Judge, and matches the output of applying \finsp on \Yeval, the
credentials, user key, and message.

@@

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      \cid \gets \adv^{\Oforgeissue}(\parm) \\
      \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 0 \\
      \textrm{Parse}~\CRED[\cid]~\textrm{as}~(\cdot,\cdot,\iid,\cdot,\cdot);~
      \IK[\iid]~\textrm{as}~((\ipk,\fissue),\cdot) \\
      (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trans[\cid]) \\
      \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
      \exists \cred \in \scred~\suchthat~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0: \\
      \pcind \pcreturn 1 \\
      \pcif \scred \neq \emptyset \land
      \nexists \uid~\suchthat~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1~
      \pccomment{\todo{New! Update proofs.}} \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of credential issuance in \UAS schemes.}
  \label{fig:exp-uas-unfor-issue}
\end{figure}
